DNSKEY Management

### 2012-12-07 paper/paper.tex
Fix date of root signing in abstract

\twocolumn[
\maketitle
\begin{onecolabstract}
  In this paper we recapitulate the current deployment status of
  DNSSEC and go into the main issues when managing its keys. This
  paper outlines the paper ``Interadministrative Challenges in
  Managing DNSKEYs'' \cite{Osterweil09} and updates some of its
  contents, especially with respect to the signing of the root zone on
  July 15, 2012. We will see that DNSSEC penetration in the Internet's 
  zones is still low, but that the necessary foundations have been lain
  for full deployment.
\end{onecolabstract}
\vspace{\baselineskip}
]

>>>>

\twocolumn[
\maketitle
\begin{onecolabstract}
  In this paper we recapitulate the current deployment status of
  DNSSEC and go into the main issues when managing its keys. This
  paper outlines the paper ``Interadministrative Challenges in
  Managing DNSKEYs'' \cite{Osterweil09} and updates some of its
  contents, especially with respect to the signing of the root zone on
  July 15, 2010. We will see that DNSSEC penetration in the Internet's 
  zones is still low, but that the necessary foundations have been lain
  for full deployment.
\end{onecolabstract}
\vspace{\baselineskip}
]
